%Format: Latex
\documentclass{article}
\setcounter{secnumdepth}{5}
\setlength{\textwidth}{17cm}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-1.5cm}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{tabulary}
\usepackage{pgfgantt}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

\tikzstyle{arrow} = [thick,->,>=stealth]

\usepackage{verbatim}
\usetikzlibrary{arrows,shapes}
\usepackage{adjustbox}
\usepackage{forest}
\usepackage{tikz-qtree}
\usepackage{soul}
\pagestyle{fancy}
\rhead{CSE\hspace{\labelsep}\textbullet\hspace{\labelsep} Autumn 2017}
\lhead{\textbf{CS302} Software Engineering}
\cfoot{\thepage}
\usepackage{indentfirst}
 \usepackage{graphicx}
\graphicspath{ {Images/} }
\setcounter{tocdepth}{5} 
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
}
\title{\textbf{CS302}\\\HUGE Software Engineering\\
\LARGE CSE\hspace{\labelsep}\textbullet\hspace{\labelsep} Autumn 2017
}

\author{\textbf{CS 03} Hexagineers}



\begin{document}
\maketitle
\line(1,0){450}

\begin{center}

\Huge\textbf{Solid Waste Management System}\\
\Large \textbf{Project Plan}
\end{center}
\newpage
\tableofcontents
\newpage
\section{Deliverables Deadlines}
\par The following table provides a brief description about the deadlines, tasks to be accomplished and the resultant deliverables.
\begin{table}[h]
\centering
\caption{Project Plan}
\label{my-label}
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{2}{|c|}{\textbf{Period}} & \multicolumn{1}{c|}{\textbf{Topic}} & \multicolumn{1}{c|}{\textbf{Deliverables}} \\ \hline
\multicolumn{1}{|c|}{\textbf{From}} & \multicolumn{1}{c|}{\textbf{To}} &  &  \\ \hline
17/08 & 31/08 & Brainstorming period & Project Idea \\ \hline
01/09 & 03/09 & Google Forms & Final Form for Survey of Customers \\ \hline
03/09 & 15/09 & Google Form Data Collection & Analysing the requirements of customers \\ \hline
12/09 & 12/09 & Survey of Scrap Dealers & Analysing the requirements of Scrap Dealers \\ \hline
16/09 & 23/09 & No Activities due to exams &  \\ \hline
24/09 & 10/10 & Survey of Industries & Analysing the requirements of Industries \\ \hline
01/10 & 10/10 & Database Design & Tables required for Database Implementation \\ \hline
01/10 & 08/10 & Prototype Design & \begin{tabular}[c]{@{}l@{}}A simple non-coded functioning app for \\ reviewing by Customers\end{tabular} \\ \hline
09/10 & 15/10 & Prototype Design Review by Customers & \begin{tabular}[c]{@{}l@{}}A review on the changes that can be made to \\ design to improve user satisfaction\end{tabular} \\ \hline
16/10 & 10/11 & Backend and Frontend Coding and Unit Testing & \begin{tabular}[c]{@{}l@{}}App for scrap dealers and a webapp of \\ an e-commerce store\end{tabular} \\ \hline
11/11 & 15/11 & Testing & A app that has minimum bugs. \\ \hline
\end{tabular}
\end{table}
\section{Team Structure}
The team structure followed is \textbf{Chief Programmer Team}.
We have one chief programmer to whom the team members report. Apart from that, we have a librarian who maintains all the documentation and communication related work.
\par The Chief Programmer is Aakash Aggarwal. Megana Ganpathiraju and Madhukar Jaisswal, Vikesh Meena and Tanmay Khandait fall under him. 
\par Tanmay Khandait and Vikesh Meena are the librarians. The work is to prepare the documentation and make sure it is reviewed by everyone in order to finalize and publish it.
\section{Team Rules}
\begin{itemize}
    \item Meet at least twice a week.
    \item Post updates on trello board and github.
    \item Deliver the deliverable before the deadline.
    \item In case of any queries or clarifications, please contact the team leader rather than making assumptions.
    \item All the members are supposed to update their blog links as an unofficial record to track the developments
\end{itemize}
\end{document}
